---
title: "Daily Macro Screener — Cross-Asset Research Desk"
author: "Quant Research"
date: "`r format(Sys.time(), '%A %d %B %Y — %H:%M %Z')`"
output:
  html_document:
    theme: cosmo
    highlight: tango
    self_contained: true
    toc: true
    toc_depth: 2
    toc_float:
      collapsed: false
      smooth_scroll: true
    css: css/dashboard.css
params:
  config_path: "config/config.yml"
  send_email: false
---

```{r setup, include=FALSE}
# =============================================================================
# Daily Macro Screener Dashboard
# Author : Quant Research Desk
# Purpose: Automated daily cross-asset dashboard for a fund operator's
#          investment committee. Pulls data from Yahoo Finance + FRED + news,
#          builds screener tables, runs tactical signals, generates narrative.
# =============================================================================

knitr::opts_chunk$set(
  echo       = FALSE,
  warning    = FALSE,
  message    = FALSE,
  fig.align  = "center",
  fig.width  = 9.5,
  fig.height = 4.5,
  cache      = FALSE,
  dev        = "png"
)

# ---- 1. Bootstrap: load libs, source modules, read config -------------------

required_pkgs <- c(
  "tidyverse", "lubridate", "scales", "stringr", "zoo", "purrr",
  "quantmod", "tidyquant", "fredr",
  "httr", "jsonlite", "rvest", "xml2",
  "plotly", "highcharter", "reactable", "gt", "kableExtra",
  "tidytext", "syuzhet", "yaml", "digest", "htmltools"
)
invisible(lapply(required_pkgs, function(p) {
  if (!requireNamespace(p, quietly = TRUE))
    install.packages(p, repos = "https://cloud.r-project.org")
  suppressPackageStartupMessages(library(p, character.only = TRUE))
}))

# Source modular code
source("R/utils.R")
source("R/data_fetchers.R")
source("R/analytics.R")
source("R/narratives.R")

# Read config
cfg <- yaml::read_yaml(params$config_path)

# ---- 2. API keys ------------------------------------------------------------
# In PRODUCTION: put keys in ~/.Renviron (created via usethis::edit_r_environ())
#   FRED_API_KEY=676d7a3632b97e47aac86ad358d746db
#   NEWSAPI_KEY=...
# Then RESTART R. The line below is for first-time / sandbox runs only.
if (nchar(Sys.getenv("FRED_API_KEY")) == 0) {
  warning("FRED_API_KEY not set — copy .Renviron.example to .Renviron and reload.")
  # Sys.setenv(FRED_API_KEY = "<your_fred_key_here>")  # one-shot only
}
log_msg("Dashboard run starting.")
```

```{r data-pull}
# =============================================================================
# 3. Data ingestion (cached, parallel-safe, error-tolerant)
# =============================================================================
hist_days <- cfg$dashboard$history_days
from_date <- Sys.Date() - hist_days

fx_prices   <- fetch_yahoo_prices(FX_TICKERS,        from = from_date,
                                  cache_key = "fx",  ttl_min = cfg$dashboard$cache_ttl_min)
com_prices  <- fetch_yahoo_prices(COMMODITY_TICKERS, from = from_date,
                                  cache_key = "com", ttl_min = cfg$dashboard$cache_ttl_min)
idx_prices  <- fetch_yahoo_prices(INDEX_TICKERS,     from = from_date,
                                  cache_key = "idx", ttl_min = cfg$dashboard$cache_ttl_min)

# Macro & rates via FRED
fred_panel <- fetch_fred_panel(FRED_SERIES, ttl_min = cfg$dashboard$fred_ttl_min)

# News + sentiment
news_df <- fetch_news(n = 25, ttl_min = cfg$dashboard$news_ttl_min)
sent    <- analyze_news_sentiment(news_df)

# Economic calendar
econ_cal <- fetch_econ_calendar(ttl_min = cfg$dashboard$econ_ttl_min)
```

```{r build-tables}
# =============================================================================
# 4. Build screener tables
# =============================================================================
fx_tbl  <- build_screener_table(fx_prices,  names(FX_TICKERS)  |> setNames(names(FX_TICKERS)))
com_tbl <- build_screener_table(com_prices, names(COMMODITY_TICKERS) |> setNames(names(COMMODITY_TICKERS)))
idx_tbl <- build_screener_table(idx_prices, names(INDEX_TICKERS) |> setNames(names(INDEX_TICKERS)))

screener <- list(fx = fx_tbl, commodities = com_tbl, indices = idx_tbl)

# Tactical analytics
signals  <- generate_tactical_signals(screener, fred_panel)
regime   <- classify_regime(
  spx_df = idx_prices[["^GSPC"]],
  vix_df = idx_prices[["^VIX"]],
  dxy_df = fx_prices[["DX-Y.NYB"]],
  hy_oas = fred_panel %>% filter(name == "hy_oas")
)
fg <- fear_greed_proxy(
  vix_df = idx_prices[["^VIX"]],
  spx_df = idx_prices[["^GSPC"]],
  hy_oas = fred_panel %>% filter(name == "hy_oas"),
  dxy_df = fx_prices[["DX-Y.NYB"]]
)
```

```{r helpers-render}
# =============================================================================
# 5. Rendering helpers
# =============================================================================
fmt_pct_cell <- function(x) {
  cls <- ifelse(is.na(x) | x == 0, "", ifelse(x > 0, "pos-cell", "neg-cell"))
  sprintf('<span class="%s">%s</span>', cls, fmt_pct(x))
}

render_screener <- function(df, price_digits = 4) {
  if (is.null(df) || nrow(df) == 0)
    return(htmltools::HTML("<em>Datos no disponibles.</em>"))

  spark_col <- reactable::colDef(
    name = "60d Trend",
    cell = function(values, index) {
      pts <- df$spark[[index]]
      if (is.null(pts) || length(pts) < 2) return("")
      htmltools::tagList(
        htmltools::tags$span(
          style = "color: var(--muted); font-family: monospace; letter-spacing: -1px;",
          paste(c("▁","▂","▃","▄","▅","▆","▇","█")[
            pmax(1, pmin(8, ceiling((pts - min(pts, na.rm = TRUE)) /
                                    (diff(range(pts, na.rm = TRUE)) + 1e-9) * 8)))
          ], collapse = "")
        )
      )
    },
    html = TRUE, minWidth = 110
  )

  reactable::reactable(
    df %>% select(asset, last, chg_d, chg_w, chg_m, chg_ytd, vol_20, drawdown, spark),
    columns = list(
      asset    = reactable::colDef(name = "Asset", minWidth = 110),
      last     = reactable::colDef(name = "Last",
                                   format = reactable::colFormat(separators = TRUE, digits = price_digits)),
      chg_d    = reactable::colDef(name = "Δ 1D",  cell = function(v) htmltools::HTML(fmt_pct_cell(v)), html = TRUE),
      chg_w    = reactable::colDef(name = "Δ 1W",  cell = function(v) htmltools::HTML(fmt_pct_cell(v)), html = TRUE),
      chg_m    = reactable::colDef(name = "Δ 1M",  cell = function(v) htmltools::HTML(fmt_pct_cell(v)), html = TRUE),
      chg_ytd  = reactable::colDef(name = "YTD",   cell = function(v) htmltools::HTML(fmt_pct_cell(v)), html = TRUE),
      vol_20   = reactable::colDef(name = "Vol 20d (ann)",
                                   format = reactable::colFormat(percent = TRUE, digits = 1)),
      drawdown = reactable::colDef(name = "DD",
                                   cell = function(v) htmltools::HTML(fmt_pct_cell(v)), html = TRUE),
      spark    = spark_col
    ),
    striped = TRUE, highlight = TRUE, compact = TRUE,
    defaultPageSize = 12, theme = reactable::reactableTheme(
      backgroundColor = "#111a2e",
      color           = "#e6ecf5",
      borderColor     = "#28324a",
      stripedColor    = "#18223a",
      highlightColor  = "#1f2b47",
      headerStyle     = list(background = "#18223a", color = "#f5a623")
    )
  )
}
```

```{r header, results='asis'}
# =============================================================================
# 6. Executive header
# =============================================================================
mood_class <- switch(regime$regime,
  "Risk-On"  = "mood-on",
  "Risk-Off" = "mood-off",
  "mood-neu"
)
cat(sprintf('
<div class="exec-header">
  <div>
    <div class="title">%s</div>
    <div class="subtitle">%s · Última actualización: %s</div>
  </div>
  <div class="mood-pill %s">Market Mood: %s</div>
</div>
', cfg$dashboard$title, cfg$dashboard$subtitle,
   format(Sys.time(), "%Y-%m-%d %H:%M %Z"),
   mood_class, regime$regime))
```

# 1. Resumen Ejecutivo

```{r exec-summary, results='asis'}
cat('<div class="highlight-box"><h3>Highlights del día</h3>\n\n')
cat(build_executive_summary(regime, signals, fg, fx_tbl, idx_tbl, sent))
cat('\n\n</div>')
```

<div class="grid">
```{r exec-cards, results='asis'}
make_card <- function(label, value, delta = NULL) {
  delta_html <- ""
  if (!is.null(delta) && !is.na(delta)) {
    cls <- ifelse(delta > 0, "pos", "neg")
    delta_html <- sprintf('<div class="delta %s">%s</div>', cls, fmt_pct(delta))
  }
  sprintf('<div class="card"><div class="label">%s</div><div class="value">%s</div>%s</div>',
          label, value, delta_html)
}
spx <- idx_tbl %>% filter(asset == "S&P 500")
dxy <- fx_tbl  %>% filter(asset == "DXY")
oil <- com_tbl %>% filter(asset == "WTI")
vix <- idx_tbl %>% filter(asset == "VIX")
ust10_last <- fred_panel %>% filter(name == "ust_10y") %>% arrange(date) %>% tail(1) %>% pull(value)

cards <- c(
  make_card("S&P 500", fmt_num(spx$last, 2), spx$chg_d),
  make_card("DXY",     fmt_num(dxy$last, 3), dxy$chg_d),
  make_card("UST 10Y", sprintf("%.2f%%", ust10_last %||% NA), NULL),
  make_card("WTI",     paste0("$", fmt_num(oil$last, 2)), oil$chg_d),
  make_card("VIX",     fmt_num(vix$last, 2), vix$chg_d),
  make_card("Fear & Greed", paste0(fg$score, " — ", fg$label), NULL)
)
cat(paste(cards, collapse = "\n"))
```
</div>

# 2. Mercado Cambiario

<div class="narrative">`r narrate_fx(fx_tbl)`</div>

```{r fx-table}
render_screener(fx_tbl, price_digits = 4)
```

```{r fx-chart}
# DXY + USDMXN dual-axis chart
dxy_df <- fx_prices[["DX-Y.NYB"]]
mxn_df <- fx_prices[["MXN=X"]]
if (!is.null(dxy_df) && !is.null(mxn_df)) {
  highchart(type = "stock") %>%
    hc_add_series(xts::xts(dxy_df$close, order.by = dxy_df$date),
                  name = "DXY", color = "#f5a623", yAxis = 0) %>%
    hc_add_series(xts::xts(mxn_df$close, order.by = mxn_df$date),
                  name = "USD/MXN", color = "#4fc3f7", yAxis = 1) %>%
    hc_yAxis_multiples(
      create_yaxis(2, height = c(2,1), turnopposite = TRUE)
    ) %>%
    hc_title(text = "DXY vs. USD/MXN — 12M") %>%
    hc_chart(backgroundColor = "#111a2e") %>%
    hc_legend(itemStyle = list(color = "#e6ecf5"))
}
```

# 3. Tasas y Renta Fija

<div class="narrative">`r narrate_rates(fred_panel)`</div>

```{r rates-table}
rates_snap <- fred_panel %>%
  filter(name %in% c("ust_2y", "ust_10y", "ust_30y", "fed_funds", "sofr")) %>%
  group_by(name) %>%
  arrange(date) %>%
  summarise(
    label = case_when(
      name == "ust_2y"    ~ "UST 2Y",
      name == "ust_10y"   ~ "UST 10Y",
      name == "ust_30y"   ~ "UST 30Y",
      name == "fed_funds" ~ "Fed Funds",
      name == "sofr"      ~ "SOFR"
    )[1],
    last_val = tail(value, 1),
    d_1d     = (tail(value, 1) - tail(value, 2)[1]) * 100,
    d_1w     = (tail(value, 1) - tail(value, 6)[1]) * 100,
    d_1m     = (tail(value, 1) - tail(value, 22)[1]) * 100,
    .groups = "drop"
  ) %>%
  select(Tenor = label, `Last (%)` = last_val,
         `Δ 1D (pb)` = d_1d, `Δ 1W (pb)` = d_1w, `Δ 1M (pb)` = d_1m)

reactable::reactable(
  rates_snap,
  columns = list(
    `Last (%)`    = reactable::colDef(format = reactable::colFormat(digits = 3)),
    `Δ 1D (pb)`   = reactable::colDef(format = reactable::colFormat(digits = 1)),
    `Δ 1W (pb)`   = reactable::colDef(format = reactable::colFormat(digits = 1)),
    `Δ 1M (pb)`   = reactable::colDef(format = reactable::colFormat(digits = 1))
  ),
  striped = TRUE, compact = TRUE,
  theme = reactable::reactableTheme(
    backgroundColor = "#111a2e", color = "#e6ecf5",
    borderColor = "#28324a", stripedColor = "#18223a",
    headerStyle = list(background = "#18223a", color = "#f5a623")
  )
)
```

```{r curve-chart}
# 2s10s slope over time
slope <- fred_panel %>%
  filter(name %in% c("ust_2y", "ust_10y")) %>%
  pivot_wider(id_cols = date, names_from = name, values_from = value) %>%
  drop_na() %>%
  mutate(slope_bps = (ust_10y - ust_2y) * 100)

if (nrow(slope) > 30) {
  plotly::plot_ly(slope, x = ~date, y = ~slope_bps, type = "scatter", mode = "lines",
                  line = list(color = "#f5a623", width = 2)) %>%
    plotly::layout(
      title = list(text = "Pendiente 2s10s (pb)", font = list(color = "#e6ecf5")),
      paper_bgcolor = "#111a2e", plot_bgcolor = "#111a2e",
      font = list(color = "#e6ecf5"),
      xaxis = list(gridcolor = "#28324a"),
      yaxis = list(gridcolor = "#28324a", zerolinecolor = "#ef4444")
    )
}
```

# 4. Commodities

<div class="narrative">`r narrate_commodities(com_tbl)`</div>

```{r com-table}
render_screener(com_tbl, price_digits = 2)
```

# 5. Índices Globales

<div class="narrative">`r narrate_equities(idx_tbl)`</div>

```{r idx-table}
render_screener(idx_tbl, price_digits = 2)
```

```{r idx-heatmap}
# Performance heatmap (chg 1D and 1W)
heat <- bind_rows(
  fx_tbl  %>% mutate(class = "FX"),
  com_tbl %>% mutate(class = "Commodities"),
  idx_tbl %>% mutate(class = "Equities")
) %>%
  select(class, asset, `1D` = chg_d, `1W` = chg_w, `1M` = chg_m) %>%
  pivot_longer(c(`1D`, `1W`, `1M`), names_to = "horizon", values_to = "ret") %>%
  mutate(horizon = factor(horizon, levels = c("1D","1W","1M")))

if (nrow(heat) > 0) {
  ggplot(heat, aes(x = horizon, y = reorder(asset, ret), fill = ret)) +
    geom_tile(color = "#28324a") +
    geom_text(aes(label = fmt_pct(ret, 1)), size = 3, color = "white") +
    scale_fill_gradient2(low = "#ef4444", mid = "#1f2b47", high = "#22c55e",
                         midpoint = 0, labels = scales::percent) +
    facet_wrap(~ class, scales = "free_y", ncol = 3) +
    theme_minimal(base_size = 11) +
    theme(
      plot.background  = element_rect(fill = "#0b1220", color = NA),
      panel.background = element_rect(fill = "#111a2e", color = NA),
      strip.background = element_rect(fill = "#18223a", color = NA),
      strip.text       = element_text(color = "#f5a623", face = "bold"),
      text             = element_text(color = "#e6ecf5"),
      axis.text        = element_text(color = "#e6ecf5"),
      panel.grid       = element_blank(),
      legend.position  = "none"
    ) +
    labs(x = NULL, y = NULL, title = "Cross-Asset Heatmap — Returns")
}
```

# 6. Correlation Matrix & PCA Macro

```{r corr-matrix, fig.height=5.5}
all_prices <- c(fx_prices, com_prices, idx_prices)
names_map <- c(setNames(names(FX_TICKERS), FX_TICKERS),
               setNames(names(COMMODITY_TICKERS), COMMODITY_TICKERS),
               setNames(names(INDEX_TICKERS), INDEX_TICKERS))
ret_mat <- build_returns_matrix(all_prices, names_map, days = 90)

if (ncol(ret_mat) > 3) {
  cm <- correlation_matrix(ret_mat)
  long <- as_tibble(cm, rownames = "x") %>%
    pivot_longer(-x, names_to = "y", values_to = "rho")
  ggplot(long, aes(x = x, y = y, fill = rho)) +
    geom_tile() +
    geom_text(aes(label = sprintf("%.2f", rho)), size = 2.6, color = "white") +
    scale_fill_gradient2(low = "#ef4444", mid = "#1f2b47", high = "#22c55e",
                         midpoint = 0, limits = c(-1,1)) +
    theme_minimal(base_size = 9) +
    theme(
      plot.background  = element_rect(fill = "#0b1220", color = NA),
      panel.background = element_rect(fill = "#111a2e", color = NA),
      text             = element_text(color = "#e6ecf5"),
      axis.text.x      = element_text(angle = 45, hjust = 1, color = "#e6ecf5"),
      axis.text.y      = element_text(color = "#e6ecf5"),
      panel.grid       = element_blank(),
      legend.position  = "right",
      legend.text      = element_text(color = "#e6ecf5"),
      legend.title     = element_text(color = "#e6ecf5")
    ) +
    labs(x = NULL, y = NULL, title = "Correlation Matrix — 90d daily returns", fill = "ρ")
}
```

```{r pca, results='asis'}
pca_out <- pca_macro(ret_mat)
if (!is.null(pca_out)) {
  cat('<div class="narrative">\n')
  cat(sprintf("**PCA cross-asset:** los 3 primeros componentes explican **%s** de la varianza ",
              fmt_pct(sum(pca_out$var_explained))))
  cat("(PC1 suele capturar el factor *risk-on/risk-off*, PC2 el factor *USD*, ",
      "PC3 el factor *duración / rates*).")
  cat('\n</div>\n')
}
```

# 7. Indicadores Macro (FRED)

```{r macro-table}
macro_snap <- fred_panel %>%
  filter(name %in% c("cpi_yoy", "core_pce_yoy", "unemployment",
                     "nfci", "consumer_conf", "hy_oas", "ig_oas")) %>%
  group_by(name) %>%
  arrange(date) %>%
  summarise(
    Indicator = c(
      cpi_yoy       = "CPI (Index)",
      core_pce_yoy  = "Core PCE (Index)",
      unemployment  = "Unemployment (%)",
      nfci          = "NFCI (Chi Fed)",
      consumer_conf = "Consumer Confidence",
      hy_oas        = "HY OAS (%)",
      ig_oas        = "IG OAS (%)"
    )[name][1],
    `Last`        = tail(value, 1),
    `Δ 1M`        = tail(value, 1) - tail(value, 2)[1],
    `Δ 12M`       = tail(value, 1) - tail(value, 13)[1],
    `Z-score 3Y`  = zscore(value, 36),
    .groups = "drop"
  ) %>%
  select(-name)

reactable::reactable(
  macro_snap,
  columns = list(
    `Last`       = reactable::colDef(format = reactable::colFormat(digits = 2)),
    `Δ 1M`       = reactable::colDef(format = reactable::colFormat(digits = 2)),
    `Δ 12M`      = reactable::colDef(format = reactable::colFormat(digits = 2)),
    `Z-score 3Y` = reactable::colDef(format = reactable::colFormat(digits = 2))
  ),
  striped = TRUE, compact = TRUE,
  theme = reactable::reactableTheme(
    backgroundColor = "#111a2e", color = "#e6ecf5",
    borderColor = "#28324a", stripedColor = "#18223a",
    headerStyle = list(background = "#18223a", color = "#f5a623")
  )
)
```

# 8. Calendario Económico (próximos días)

```{r econ-cal}
if (is.null(econ_cal) || nrow(econ_cal) == 0) {
  cat("<em>Calendario económico no disponible (fuente externa).</em>")
} else {
  reactable::reactable(
    econ_cal,
    striped = TRUE, compact = TRUE, searchable = TRUE, defaultPageSize = 12,
    theme = reactable::reactableTheme(
      backgroundColor = "#111a2e", color = "#e6ecf5",
      borderColor = "#28324a", stripedColor = "#18223a",
      headerStyle = list(background = "#18223a", color = "#f5a623")
    )
  )
}
```

# 9. Noticias y Sentiment

<div class="narrative">`r sent$summary`</div>

```{r news-render, results='asis'}
if (nrow(sent$scored) > 0) {
  scored <- sent$scored %>% arrange(desc(abs(sentiment))) %>% head(10)
  for (i in seq_len(nrow(scored))) {
    chip_class <- switch(scored$label[i],
      "Bullish" = "chip bull",
      "Bearish" = "chip bear",
      "chip"
    )
    cat(sprintf('<div class="news-item">
      <span class="%s">%s</span>
      <span class="src"> · %s · %s</span><br/>
      <a class="title" href="%s" target="_blank">%s</a>
    </div>\n',
      chip_class, scored$label[i],
      scored$source[i] %||% "Source",
      ifelse(is.na(scored$published[i]), "",
             format(scored$published[i], "%Y-%m-%d %H:%M")),
      scored$url[i] %||% "#", scored$title[i]))
  }
}
```

```{r news-words, fig.height=3.5}
if (nrow(sent$top_words) > 0) {
  ggplot(sent$top_words, aes(x = reorder(word, n), y = n)) +
    geom_col(fill = "#f5a623") +
    coord_flip() +
    theme_minimal(base_size = 11) +
    theme(
      plot.background  = element_rect(fill = "#0b1220", color = NA),
      panel.background = element_rect(fill = "#111a2e", color = NA),
      text             = element_text(color = "#e6ecf5"),
      axis.text        = element_text(color = "#e6ecf5"),
      panel.grid       = element_line(color = "#28324a")
    ) +
    labs(x = NULL, y = NULL, title = "Términos más frecuentes — feed de noticias")
}
```

# 10. Señales Tácticas

```{r signals-render, results='asis'}
cat('<div class="grid">\n')
for (s in unlist(signals)) {
  cls <- ifelse(grepl("Bullish|Strength|Attractive|On|Compression", s), "chip bull",
         ifelse(grepl("Bearish|Weakness|Off|Expansion|Inverted|Weakening", s), "chip bear",
                "chip"))
  cat(sprintf('<div class="card"><span class="%s">%s</span></div>\n', cls, s))
}
cat('</div>\n')
```

```{r fg-gauge, fig.height=3}
plotly::plot_ly(
  type = "indicator", mode = "gauge+number",
  value = fg$score,
  title = list(text = paste0("Fear & Greed Proxy — ", fg$label),
               font = list(color = "#f5a623", size = 16)),
  gauge = list(
    axis = list(range = list(0, 100), tickcolor = "#e6ecf5"),
    bar = list(color = "#4fc3f7"),
    steps = list(
      list(range = c(0,20),  color = "#ef4444"),
      list(range = c(20,40), color = "#f97316"),
      list(range = c(40,60), color = "#94a3b8"),
      list(range = c(60,80), color = "#22c55e"),
      list(range = c(80,100), color = "#16a34a")
    )
  )
) %>% plotly::layout(
  paper_bgcolor = "#0b1220",
  font = list(color = "#e6ecf5")
)
```

# 11. Postura de Mercado — Cierre del Comité

```{r posture, results='asis'}
post <- build_market_posture(regime, signals, fred_panel, fg)
cat('<div class="highlight-box"><h3>Narrativa dominante</h3>\n\n')
cat(post$narrative)
cat('\n\n<h3 style="margin-top:18px;">Riesgos a monitorear</h3>\n<ul>')
for (r in post$risks) cat(sprintf("<li>%s</li>", r))
cat('</ul></div>')
```

```{r simple-var, results='asis'}
spx_df <- idx_prices[["^GSPC"]]
if (!is.null(spx_df) && nrow(spx_df) > 30) {
  px <- as.numeric(spx_df$close)
  px <- px[!is.na(px) & px > 0]
  if (length(px) > 30) {
    spx_rets <- diff(log(px))
    v95 <- simple_var(tail(spx_rets, 252), 0.05)
    v99 <- simple_var(tail(spx_rets, 252), 0.01)
    cat(sprintf('<div class="narrative"><b>VaR paramétrico simple (S&P 500, 1d, 1Y):</b> 95%% = %s, 99%% = %s.</div>',
                fmt_pct(v95), fmt_pct(v99)))
  } else {
    cat('<div class="narrative">VaR no disponible: datos insuficientes de S&P 500.</div>')
  }
} else {
  cat('<div class="narrative">VaR no disponible: S&P 500 no se descargó correctamente.</div>')
}
```

<div class="footer">
  Generado automáticamente por <b>Daily Macro Screener</b> · `r format(Sys.time(), '%Y-%m-%d %H:%M %Z')`<br/>
  Fuentes: Yahoo Finance, FRED, Reuters / NewsAPI, Investing.com Economic Calendar.<br/>
  Documento de uso interno. No constituye recomendación de inversión.
</div>

```{r save-output, include=FALSE}
# Save the rendered HTML to output/reports/ with a date stamp.
# (rmarkdown::render() itself writes the output, but we also persist a stamped copy.)
log_msg("Dashboard rendered successfully.")
```
